Safe Transferable Regions

### 2016-07-03 paper/type-system.tex
More comments on syntax.
Commentary updates.

\dv{Why do we have the type parameters of $a$ and $b$ extending \C{Object} versus
  the actual class extending \C{Object<$\rho^a$>}? Also, instead of explicitly introducing
  all those $\rho^a$ variables, wouldn't it be nicer if we overloaded \C{this} to be a valid region,
  meaning {\bf the} region of this object? I think notationally that might be more lightweight?}

@@

The type rule for \C{new \RgnZ} expressions expects the \RgnZ class's
constructor to be called with a nullary function that returns a value
in its allocation context. It enforces this by typechecking the body
($e$) of the function under an empty context containing nothing but
the allocation context of the function. This step ensures that the
value returned by the function stores no references to objects
allocated elsewhere, including the top region ($\toprgn$), thus
preventing cross-region references originating from transferable
regions\footnote{The body of the function ($e$) might, however, create
new (transferable) regions while execution, but that is fine as long
as such regions, and objects allocated in them, don't find their way
into the result of evaluating $e$}.

@@

The supplement defines a small-step operational semantics for \fbname
via a five-place reduction relation:
\vspace*{-0.15in}
\begin{smathpar}
  \redstoo{(e,\rhomap)}{(e',\rhomap')}
\end{smathpar}
The reduction judgment should be read as following: given a set
($\rhoenv$) of regions that are currently live, and a map ($\rhomap$)
from unique identifiers of transferable regions to their current
states (Fig.~\ref{fig:region-fsm}), the expression $e$ reduces to
$e'$, while updating $\rhomap$ to $\rhomap'$. The semantics gets
``stuck'' if $e$ attempts to access an object whose allocation region
is not present in $\rhoenv$, or if $e$ tries to \C{open} a
transferable region, whose identifier is not mapped to a state by
$\rhomap$.  On the other hand, if $e$ attempts to commit an operation
on a $\RgnZ$ object that is not sanctioned by the transition
discipline in Fig.~\ref{fig:region-fsm}, then it raises an exception
value ($\invalidexn$).

>>>>

\dv{Explain why do we have the type parameters of $a$ and $b$ extending \C{Object} versus
  the actual class extending \C{Object<$\rho^a$>}? What is the point of having it in \C{Object<$\rho^a$>?}.
  I think it does not make sense to include it there, exactly as we do not include regions in the type parameters,
  it's all about the type inheritance hierarchy. A second point: instead of explicitly introducing
  all those $\rho^a$ variables, wouldn't it be nicer if we overloaded \C{this} to be a valid region,
  meaning {\bf the} region of this object? I think notationally that might be more lightweight?}

@@

The type rule for \C{new \RgnZ} expressions expects the \RgnZ class's
constructor to be called with a nullary function that returns a value
in its allocation context. It enforces this by typechecking the body
($e$) of the function under an empty context containing nothing but
the allocation context of the function. This step ensures that the
value returned by the function stores no references to objects
allocated elsewhere, including the top region ($\toprgn$), thus
preventing cross-region references originating from transferable
regions\footnote{The body of the function ($e$) might, however, create
new (transferable) regions while execution, but that is fine as long
as such regions, and objects allocated in them, don't find their way
into the result of evaluating $e$}. \dv{Which one is that rule? If it's the upper
  left rule, is there a typo? What is it's type? What is the context?}

@@

The supplement defines a small-step operational semantics for \fbname
via a five-place reduction relation:
%\vspace*{-0.15in}
\begin{smathpar}
  \redstoo{(e,\rhomap)}{(e',\rhomap')}
\end{smathpar}
The reduction judgment should be read as following: given a set
($\rhoenv$) of regions that are currently live, and a map ($\rhomap$)
from unique identifiers of transferable regions to their current
states (Fig.~\ref{fig:region-fsm}), the expression $e$ reduces to
$e'$, while updating $\rhomap$ to $\rhomap'$. The semantics gets
``stuck'' if $e$ attempts to access an object whose allocation region
is not present in $\rhoenv$, or if $e$ tries to \C{open} a
transferable region, whose identifier is not mapped to a state by
$\rhomap$.  On the other hand, if $e$ attempts to commit an operation
on a $\RgnZ$ object that is not sanctioned by the transition
discipline in Fig.~\ref{fig:region-fsm}, then it raises an exception
value ($\invalidexn$).
